%!TeX root = main.tex
\chapter{Literature Survey}

\section{Existing Systems}
The domain of interview preparation has seen various technological interventions, ranging from simple question banks to more sophisticated mock interview platforms. Early systems focused primarily on static content delivery, providing users with lists of common interview questions and model answers. While useful, these systems lacked the interactivity crucial for effective preparation.

More recent platforms have incorporated video recording features, allowing users to record their responses and review them later. However, many of these solutions rely on peer review or paid mentorship for feedback, which can be inconsistent or expensive.

\section{AI in Education and Recruitment}
The integration of Artificial Intelligence (AI) into education and recruitment has transformed how candidates prepare for interviews.
\begin{enumerate}
    \item \textbf{Automated Resume Screening}: Application Tracking Systems (ATS) use keyword matching and semantic analysis to filter resumes. Understanding these algorithms is critical for job seekers.
    \item \textbf{Conversational AI}: Large Language Models (LLMs) like GPT-4 and Google Gemini enable natural language interactions, allowing for dynamic question generation and context-aware feedback \cite{aceit_paper}.
    \item \textbf{Emotion Analysis}: Advanced systems now incorporate computer vision and audio analysis to evaluate non-verbal cues such as eye contact, facial expressions, and voice modulation, providing a holistic assessment of a candidate's performance.
\end{enumerate}

\section{Gap Analysis}
Despite these advancements, there remains a gap in comprehensive platforms that integrate all aspects of interview preparation—technical coding practice, behavioral interviews, and resume optimization—into a single, cohesive experience. Most existing tools focus on one specific area (e.g., LeetCode for coding, Pramp for mock interviews), forcing users to juggle multiple platforms. AceIt aims to fill this void by offering an all-in-one solution powered by state-of-the-art AI.
